\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[12pt,oneside]{krantz}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={The Four Bad Guys},
            pdfauthor={Beckett Stephens},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{booktabs}
\usepackage{caption}
\captionsetup[figure]{labelformat=empty}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\title{The Four Bad Guys}
\providecommand{\subtitle}[1]{}
\subtitle{Book 5}
\author{Beckett Stephens}
\date{2018-11-25}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{1}
\tableofcontents
}
\hypertarget{preface}{%
\chapter*{Preface}\label{preface}}


This book is about my adventures in a video game named Minecraft.

\hypertarget{about-the-author}{%
\chapter*{About the Author}\label{about-the-author}}


Beckett Stephens is an aspiring author and illustrator. \emph{Herobrine
Returns} is his third published work. Beckett also loves Minecraft,
Lego's, and Transformers, as well as making up endless stories while he
walks. He currently lives in Maryland with his younger brother.

\hypertarget{acknowledgements}{%
\chapter*{Acknowledgements}\label{acknowledgements}}


Thanks to Dad for helping me publish \emph{The Four Bad Guys} online.
Also, thanks to Minecraft community for the inspiration that helped me
make this book.

\hypertarget{maleks-old-friend}{%
\chapter{Malek's old friend}\label{maleks-old-friend}}

Someone was running someone was panicking whose name was Ender. He led a
company called end spies. Their job was To spy on bad guys. but right
now they were being hunted. right now and there was running because End
Bots Three Hunters were chasing him. Ender ran so fast that the bad guys
didn't know where he went. soon and her came to a wall of iron bars
protecting our base. Ender said,'' let me in! let me in!'' There was a
security camera. I saw him over the security camera. I said,'' Malik you
have to see this.'' Malik came and said,'' that sander! Let him in!!'' I
did. We close the door when the three bad guys returned. Alex put up the
defenses. the bad guy in the middle said,'' you don't scare us''
Clank!!! The other two bad guys had drop their weapons and ran away. ``
AAAAAAAAAAAA!!!!!!'' Scream the other bad guy as he ran away. `` that
was easy.'' Said Ender. ``now tell us why you're here.'' I said. `` I
will'' said Ender

\hypertarget{two-villains}{%
\chapter{Two villains}\label{two-villains}}

After book 4 (Herobrine returns) king zombie took control of the bad
guys, he's trying to find more leaders to help him. he was looking for a
witch named Ave that helped him a long, long, long, time ago. He sent
EndBot And his helpers to look for her. just then Ding dong king zombie
said,'' who is it.'' `` it Ave.'' Ave said. ``come in.'' said king
zombie. Ave walked in and said,'' it's good to be back.'' thanking
zombie said,'' Ave, you are now a boss for the bad guys, step closer to
receive your red violet badge and your black armor.'' Ave step closer
and got her stuff. Just then Commander rip said,'' king zombie you have
to see this!'' out the window there was someone flying towards the gate.
it was Endy.

\hypertarget{enders-story}{%
\chapter{Ender's story}\label{enders-story}}

Everybody found a seat and sat down. I said'' Ender, I want to hear your
backstory. what brought you here.'' Ender said,'' well first, I made a
network of spies from the end we call ourselves the end spies. we know
that Malik likes to spy on other bad guys.'' `` wait you did'' asked
Malik. `` we did. one day A bad guy named Armstrong figured out that
Malik likes to spy on other bad guys.He ordered me to destroy him. But
instead we escaped and blew up the base and every bad guy died except
one, Armstrong. somehow he survived but he was really hurt he couldn't
see out of his left eye and he had no feeling in his right arm So they
will replace with robot parts. ever since that all of our bases have
been Hunted and now I'm the only Survivor.'' Ender started to cry. I
said,'' Ender I'm sorry you can live with us.'' Felix said,'' Beckett
are you sure?'' `` yes I'm sure.'' I said

\hypertarget{endy}{%
\chapter{Endy}\label{endy}}

There Endy the Ender Dragon. king zombie said,''open the gate, let Endy
in.'' he landed outside the door when king zombie ran out and said,''
Endy, what brings you here?'' Endy said with a growl,'' I want to see a
Ave!!!'' Just then ave ran out the door . endy said,'' 2 years ago King
ass took control of all the bad guys I knew that the bad guys we're
going to die so I quit and promise to return When I was needed. so I
left today I woke up with a plan, Ave, use your powers to make me
stronger, faster, eviler.'' `` sure.'' said Ave pleased.

\hypertarget{the-power}{%
\chapter{The power!!!}\label{the-power}}

Ave called three more witches, Ave said,'' look in page 61 in witch
spells.'' they found it and looked at the blueprint. it looked like it
this: they got ready ave said to Endy,'' this really hurts a lot,
remember that.'' Endy said,''start.'' They did. endy screamed as he felt
himself getting stronger and stronger and stronger. soon his eyes turn
red then the witches stopped. `` how do you feel Endy?'' asked Ave. ``
haha. perfect.'' dead Endy in an evil voice.

\hypertarget{our-cool-spaceships}{%
\chapter{Our cool spaceships}\label{our-cool-spaceships}}

Meanwhile at my base\ldots{}

`` I'm done!!!'' Alex said. We ran over. it was a spaceship for the
water, fire, night, and life God. `` wow!'' everybody said. Alex said,''
oh that's nothing. come with me.'' my team walk down the hall and walked
in a door and saw a big battleship. `` what!!!'' Everybody screamed. ``
I'm still working on it it should be done by the end of this book.''
Alex said. I said,'' don't spoil the book.'' beep! beep! beep! `` it's
time to go on patrol. Bye everybody see you soon.'' I said. I got into
the amazing life ship and flew away. just then, Ender came back from his
time spying on the bad guys and said,'' where's Beckett?!?'' `` Oh he
just went on Patrol.'' `` no'' said Ender. `` what'' asked Felix. Ender
said,'' Beckett is going to be\ldots{}''

\hypertarget{chapter-6-and-the-plan}{%
\chapter{Chapter 6 and ½: the plan}\label{chapter-6-and-the-plan}}

sorry that I had to interrupt that chapter but there is something I need
to tell you:

15 minutes earlier\ldots{}

The bad guy set up a meeting. king zombie said,''Endy, you said you had
a plan.'' `` yes,'' said Endy `` instead of fighting Beckett's whole
team will just fight Beckett. then we'll fight the rest of the team,
then will suck the life gems magic and use it to take over. Hahaha!''
``Great idea. to keep the good guys busy I will send Commander
Armstrong.'' King zombies said. he called Commander Armstrong and sent
him to my base. Ender saw this all and ran away.

\hypertarget{chapter-6-and-our-cool-spaceships-in-progress}{%
\chapter{Chapter 6 and ¾: our cool spaceships ( in
progress)}\label{chapter-6-and-our-cool-spaceships-in-progress}}

``\ldots{} Hunted by Endy the Ender Dragon, king zombie and Ave the
witch! we need to find him, and fast! Alex open the door when\ldots{}
Zap!! A Blu-ray shut down I was close the door before it got inside ``
who did that?!?'' Alex asked to herself

\hypertarget{armstrong}{%
\chapter{Armstrong}\label{armstrong}}

EnderRan to the camera. he said,'' Armstrong! he did that!'' Armstrong
blue in the spaceship. Suddenly arms came out of spaceship. one arm was
holding a machine called ``the hypnotizer''

Meanwhile, I was being chased by Endy, Ave and king zombie. suddenly a
slot open that you put the life sword in. I did. Just then a giant sword
formed on top of my spaceship. `` perfect.'' I said. I thought the bad
guys but they still chased me. meanwhile, Armstrong was attacking Felix,
Malik, Alex, mom, and Ender. Felix, Malik and Mom were flying and
spaceships. Alex and Ender War inside my base Armstrong hit the base
with his hypnotizer and everyone inside got hypnotized (Alex andEnder.)
next he hit mom and then Malik. Then and Felix the Spy ship a slot open
that you put the fireball shooter in. Felix did. suddenly, a huge
fireball shooter formed on top of Felix's Fire Ship. Felix pressed the
button and the fireball shooter shot a fireball. It hit the bad guys
spaceship but Armstrong escaped. meanwhile the bad guys were still
chasing me. they want right above me and sucked me in with a tractor
beam.'' oh no.'' I said sadly

\hypertarget{captured}{%
\chapter{Captured}\label{captured}}

They put me in a cell.'' Set a course for Beckett's base.'' King zombies
dead. I sat in my cell then Heard a Voice ``hey, Beckett it's me the
life gem. I'm very proud of you that. AAAAAAAAAAAAA!!!'' I heard Ave
from out the door,'' I successfully sucked the magic out of the life
gem.'' I put my head down I started to cry. ``no.'' I said. but I felt
like I he was still alive and he was. you see the life gem was being
recharged by me, I didn't know how at the time but eventually the tank
that was holding too much magic and got too full and shut down the
sucker. the life gem got free. it hop to me and then I turned into the
Life God and said,'' I look different.'' the life gem said,'' that means
you can shoot a tree out of your hand.'' `` cool.'' I said. then I cut
the bars using my life sword. Then I ran to my life ship and escaped.
then I formed the life on top of my life ship and cut the spaceship. it
crashed in front of my base

\hypertarget{endys-last-breath}{%
\chapter{Endy's last breath}\label{endys-last-breath}}

Mom said,'' Malik and I will chase king zombie, Ave, and Armstrong.
Felix, Beckett defeat Endy.'' and they ran away. me and Felix got in our
spaceships and started fighting Endy. but endy was faster than our
spaceships, could heal very fast, and was very, very strong. Endy hit
our spaceships so hard with his tail our spaceships fell to the ground.
`` oh no.'' I said `` it is all over'' sad Felix. then we heard this:
Screech!!!! A few seconds later we saw Alex's big battleship! Alex
said,'' I told you it would be ready at the End of This Book. Now, let's
go fight Endy.'' I said,'' okay.'' Endy Attacked but he could hardly
make a dent in it before he got hurt. Endy was so distracted by the
battleship that he didn't see me in my spaceship. I formed the sword on
top of my spaceship and I cut it in more and more damage came to Endy.
eventually he fell to the ground. when the dust cleared Endy was no
more.

\hypertarget{big-fight}{%
\chapter{Big fight}\label{big-fight}}

King zombie crashed and when he woke up he saw Felix.'' Well well well.
look who's here.'' Felix said,'' I am here to finish the job. soon you
will be no more.'' Felix turn into the fire god. king zombie got out his
weapon the fire sword. they fought. Felix wasn't getting anywhere but he
was dodging all King zombies attacks. then he formed the fireball
shooter and shot of Fireball. king zombie Dodge all of these. but one of
them hit his sword. Felix kept firing more and more Fireballs at King
zombies sword. then the fire sword flew out of King zombies hands. ``
no!'' king zombie Said. Felix and king zombie ran to get the sword.
Felix got it first. then he sliced King zombies head but king zombie
survived. Felix said,'' I win.'' and he walked away. Ave came and helped
king zombie up. Armstrong, Ave, and king zombie went away. But Endy
stayed to finish the job

\hypertarget{the-portal}{%
\chapter{The portal}\label{the-portal}}

A few hours later, Ave said,'' we may have lost Endy but we still have
tons of Life gem Magic, more than I ever thought was possible. I think I
can build a portal that will send the good guys galaxies away.'' so
that's what she did. 4 days later\ldots{} Ave Launch the portal. We saw
the portal and Alex wanted to go on a ride in the spaceship. she got to
ride with Malik. it was a hard fight. And at the end the portal was
going to suck up the Gods. From a distance Ave what shooting post
arrows. these arrows suck up Magic. Felix and me and Malik and Alex and
Mom were all being sucked closer to the portal. when a turbo Switch
opened on Felix's dashboard. Felix Pressed the button and got loose of
the portals grip. but then Felix heard me say,'' goodbye, Felix.'' as
me, Alex, Malik, and Mom were all sucked in. Felix said,'' no!'' Felix
started to cry. he had no idea what he was going to do next.

sorry there will be no more books of this series. no more not at all.
who am I kidding, I will make tons more. So find out where I am in my
Nextbook

\textbf{two Adventures} \emph{my sixth book}

\end{document}
